Well-quasi-orderings on word languages

### 2025-10-14 src/infixes.tex
new: proof sketch that everything works out

    \todo[inline]{Aliaume: proof of concept proof}
    Let us now conclude that the same $x,y$ work for all $\vec{n} \in \Nat^k$.

>>>>

    \todo[inline]{Aliaume: proof of concept proof} Let us now conclude that the
    same $x,y$ work for all $\vec{n} \in \Nat^k$. The reasoning is that if
    $w[\vec{n}]$ is of the form $u_1 x^p x'$ where $x' \prefleq x$, and $x$ is
    primitive (not a power of a smaller word), then all the iterated words
    $v_i^{n_i}$ must be powers of a conjugate of $x$ (cyclic shift of $x$), and
    all the $u_i$'s must be such that the concatenation of the $u_i$'s and
    $v_i$'s align properly with $x$. Since the length of $x$ is at most $\min
    \setof{\card{v_i}}{1 \leq i \leq k}$, we conclude that the $v_i$'s
    themselves are powers of a conjugate of $x$, and that the $u_i$'s are
    suffixes or prefixes of $x$. Now, we conclude that all the words
    $w[\vec{n}]$ are of the correct form. Similar reasoning applies for the
    other two cases.
